---
title: "30-feature-engineering"
output: html_notebook
---
```{r}
library(glue)
```


## Count of Services
The current data structure does not make it easy to understand how many services a customer is subscribed to. They are a mixture of logical and string fields with different values. The thought is that the more services someone subscribe to, the more resistant they might be to cancel/churn.
Thought: The more services one subscribes to, the less likely they are to churn.
```{r}
serivce_columns <- c("phone_service", "internet_service", "online_security", "online_backup", 
                     "device_protection", "tech_support", "streaming_tv", "streaming_movies")

service_count <- function(df, col_vector) {
  column_check <- ifelse(col_vector %in% names(df),TRUE, FALSE)
  
  if(FALSE %in% column_check) {
    bad_columns <- paste(col_vector[!column_check],collapse=", ")
    stop(glue("Error - The following column(s) were not found in the data frame:\n {bad_columns}"))
  }
  
  df %>% 
    mutate(
      tmp_internet_service = ifelse(!internet_service == "no", 1, 0),
      tmp_online_security = ifelse(online_security == "yes", 1, 0), 
      tmp_online_backup = ifelse(online_backup == "yes", 1, 0), 
      tmp_device_protection = ifelse(device_protection == "yes", 1, 0),
      tmp_tech_support = ifelse(tech_support == "yes", 1, 0),
      tmp_streaming_tv = ifelse(streaming_tv == "yes", 1, 0),
      tmp_streaming_movies = ifelse(streaming_movies == "yes", 1, 0)) %>% 
    mutate(count_services = rowSums(.[grep("^tmp|^phone_service$", names(.))])) %>% 
    select(everything(), -grep("^tmp", names(.)))
}

# Executing Function
telco_churn_clean <- service_count(telco_churn_clean, serivce_columns)

# Test - Value Within Expected Range
telco_churn_clean %>% 
  assert(within_bounds(1, 8), count_services)
```


## Percent of Available Services Subscribed
Of the possible services offered, what percentage did the customer subscribe to. If they subscribe to interent, there are 8 possible services. If they do not subscribe to interent, there are only 2 possible services (phone, internet).
Thought: The more services one subscribes to, the less likely they would be to churn.
__Note__ - This makes the assumption that every customer had the option of an internet subscription.
```{r}
percent_services_subscribed <- function(df, 
                                        phone = phone_service, 
                                        internet = internet_service, 
                                        count_service = count_services) {
  df %>% 
    mutate(perc_services_subscribed = {{count_service}} / 
             ifelse(!{{internet}} == "no", 8, 2))
}

# Executing Function
telco_churn_clean <- percent_services_subscribed(telco_churn_clean, phone_service, internet_service, count_services)

# Test 1 -- Did subscribe to internet. Eight possible subscriptions
telco_churn_clean %>% 
  filter(!internet_service == "no") %>%
    assert(in_set(.125, .25, .375, .5, .625, .75, .875, 1), perc_services_subscribed)

# Test 2 -- Did not subscribe to internet. Only two possible subscriptions
telco_churn_clean %>% 
  filter(internet_service == "no") %>%
    assert(in_set(.5, 1), perc_services_subscribed)
```